---
title: "Study 1: Results Overview"
floatsintext : yes
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 2
    toc_float: true
    highlight: pygments
    code_folding: hide
    css: table-style.css
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
set.seed(1234)

if (!require("pacman")) install.packages("pacman");
library(pacman)
pacman::p_load(here, MASS, svglite, ggplot2, papaja, lavaan, tidyverse, knitr, kableExtra, codebook, psych, rlang, bfrr)

wd <- getwd()
if (!dir.exists("clean_data")) {dir.create(file.path(wd, "clean_data"))}
if (!dir.exists("figures")) {dir.create(file.path(wd, "figures"))}

knitr::opts_chunk$set(echo = TRUE, cache = TRUE, warning = FALSE, message = FALSE, autodep = TRUE, fig.path = "figures/")
options(mc.cores = parallel::detectCores(), ## Run chains in parallel
        knitr.kable.NA = "") ## Don't show NAs in tables
ggplot2::theme_set(theme_apa() +
                     theme(plot.caption = element_text(hjust = 0),
                           plot.caption.position =  "plot",
                           plot.title.position = "plot"))

export <- haven::read_spss(here("raw_data/01_EXPORTED.sav"))
```

```{r data-cleaning, include=FALSE}
export[, c(2:5, 15, 17)] <- haven::as_factor(export[, c(2:5, 15, 17)])

raw <- export %>%
  mutate(att_checkbi = ifelse(att_check == 3, 1, 0) %>% as_factor(.),
         condition = as_factor(export$condition) %>% set_attrs(., labels = c("dynamic" = 1, "static" = 2, "none" = 3)) %>% relevel(., "dynamic"),
         expintent_avg = rowMeans(across(intention_1:expectation_1), na.rm = T),
         cons_proj = select(., cons_now_perc_1, cons_next_perc_1, cons_six_perc_1) %>% rowMeans(., na.rm = TRUE),
         genderbi = na_if(gender, "Other") %>% droplevels() %>% recode_factor(., "Male" = -1, "Female" = 1),
         conformity_3 = 8 - conformity_3,
         conformity_mean = rowMeans(select(., starts_with("conformity_")), na.rm = TRUE),
         age_c = age - mean(age, na.rm = TRUE)) %>%
  rename_with(., .fn = ~ str_remove(., "_1"), .cols = c(interest_1:politics_1, meat_cons_1))

# excluding vegetarians and attention check fails
#complete <- raw %>% filter(att_check == 1)
complete <- raw %>% filter(!is.na(conformity_1))
noveg <- complete %>% filter(veg != "Yes")

# excluding unneeded fields
clean <- noveg %>%
  select(-RecordedDate, -veg, -att_check) %>%
  mutate(condition = relevel(condition, "dynamic"),
         cons_proj_c = cons_proj - mean(cons_proj), #centering projected cons
         conformity_mean_c = conformity_mean - mean(conformity_mean)) %>% #centering conformity
  cbind(., psych::dummy.code(.$condition))

# outliers
mcd     <- cov.mcd(clean[,c(5:13, 17:22)], quantile.used = nrow(clean[,c(5:13, 17:22)])*.75)
mcd_mah <- mahalanobis(clean[,c(5:13, 17:22)], mcd$center,mcd$cov)
cutoff  <- qchisq(p = 0.99, df = ncol(clean[,c(5:13, 17:22)]))
no_out  <- clean[mcd_mah <= cutoff, ]

saveRDS(clean, file = "clean_data/clean.rds")
saveRDS(no_out, file = "clean_data/no_out.rds")
haven::write_sav(clean, "clean_data/clean.sav")

# correlation
mcor = cor(clean[,c(5:6, 24, 15, 25, 27)], use = "pairwise.complete.obs")
symnum(mcor)

##assumption set up
random = rchisq(nrow(clean), 7)
fake = lm(random ~., data = clean[ , -1])
standardized = rstudent(fake)
fitted = scale(fake$fitted.values)

assumptions <- list(additivity = cor(mcor[ , -1]) %>% symnum(),
                    homogeneity = plot(fitted, standardized) + abline(0,0) + abline(v = 0), ##homog and s
                    normality = hist(standardized), ##multivariate normality
                    linearity = qqnorm(standardized)) ##multivariate linearity
```

```{r data-overview, include=FALSE}
describeBy(clean, clean$condition) # check distribution and normality

# participants
data_desc <- c(total_n = nrow(raw),
               incomp_n = nrow(raw) - nrow(complete),
               veg_n = nrow(complete) - nrow(noveg),
               clean_n = nrow(clean)) 
# age
age_desc <- clean %>%
  summarise(min_age = min(age),
            max_age = max(age),
            m_age = printnum(mean(age)),
            sd_age = printnum(sd(age)))
# gender
gender_freq <- round(100 * prop.table(table(clean$gender)), digits = 2)

# outcomes
measure_sum <- clean %>%
  summarise(m_interest = mean(interest),
            m_attitude = mean(attitude),
            m_int_exp = mean(expintent_avg),
            m_cons = mean(meat_cons),
            m_cons_proj = mean(cons_proj),
            m_conformity = mean(conformity_mean, na.rm = T),
            sd_interest = sd(interest),
            sd_attitude = sd(attitude),
            sd_int_exp = sd(expintent_avg),
            sd_cons = sd(meat_cons),
            sd_cons_proj = sd(cons_proj),
            sd_conformity = sd(conformity_mean, na.rm = T))

# reliability
cron <- clean %>% select(conformity_1:conformity_6) %>% psych::alpha() # scale reliability

# correlation matrix
measure.tib <- tibble(Measure = c("1. Interest", "2. Attitude", "3. Intention/Expectation", "4. Own consumption", "5. Projected consumption", "6. Conformity"),
                      Mean = unlist(measure_sum[, 1:6]),
                      SD = unlist(measure_sum[, 7:12])) %>%
  cbind(., mcor) %>% select(-conformity_mean) %>% remove_rownames() 
```

# Methods {.tabset .tabset-pills}

## Design and procedure

A double blind, between-participants experimental design was employed in
the study. The study was presented as a survey on attitudes toward meat
consumption. All participants were directed from their recruitment
platform to a Qualtrics survey. There were 3 conditions. In the
experimental condition, participants read a normative statement
depicting a trending minority norm. In the control conditions,
participants either read a statement depicting a minority norm, or did
not read any text and so proceeded to the dependent measures without an
intervening task.

After participants read the statements, they completed dependent
measures relating to meat consumption, followed by demographic questions
and a measure of conformity.

## Participants

A total of `r data_desc[[1]]` participants were recruited through a
survey posted on Prolific. `r data_desc[[2]]` were excluded due to
incomplete responses, and `r data_desc[[3]]` were excluded as they are
vegan/vegetarian. Using a robust Mahalanobis distance based on the
Minimum Covariance Determinant, `r nrow(clean) - nrow(no_out)`
multivariate outliers were detected and removed. The final sample (*N* =
`r data_desc[[4]]`) ranged in age `r age_desc$min_age` to
`r age_desc$max_age` (*M~age~* = `r age_desc$m_age`, *SD~age~* =
`r age_desc$sd_age`). The participants were predominantly female
(`r gender_freq[2]`%). The participants received £0.35 (\$0.45) for
successfully completing the task.

## Normative statements

**Trending norm.** In the trending norm condition, the text read:
'Research from early 2020 has found that 48% of British people engage in
one or more of the following behaviours:

• Eating small portions of meat • Opting out of eating meat several days
of the week • Adopting a vegan/vegetarian diet

This has increased from 37% in 2018.'

**Minority norm.** In the minority norm condition, the text read:
'Research from early 2020 has found that 48% of British people engage in
one or more of the following behaviours:

• Eating small portions of meat • Opting out of eating meat several days
of the week • Adopting a vegan/vegetarian diet'

**No norm control.** The no norm control condition did not have any
text.

## Measures

**Demographic questions.** Participants answered questions relating to
their demographic characteristics (e.g., age, gender, political
position; see Appendix A).

**Dependent measures.** We measured interest in eating less meat,
attitudes towards eating meat, intentions and expectations to limit own
meat consumption. Additionally, we measured expectations about future
meat consumption. All primary outcomes were measured using single item
measures.

*Interest.* To measure interest in limiting meat consumption,
participants responded to the statement: "I am interested in eating less
meat" on a 0-100 scale (0 = Not at all interested, 50 = Somewhat
interested, 100 = Extremely interested).

*Attitudes.* To measure attitudes, participants responded to the
statement: "My attitude towards eating less meat is..." on a 0-100
slider scale (0 = Extremely unfavourable, 50 = Neither unfavourable nor
favourable, 100 = Extremely favourable).

*Intentions.* To measure intentions, participants responded to the
statement: "I intend to eat less meat within the next year" on a 0-100
slider scale (0 = Very strongly disagree, 50 = Neither agree nor
disagree, 100 = Very strongly agree).

*Expectations*. To measure expectations, participants responded to the
statement: "I expect to eat less meat within the next year" on a 0-100
slider scale (0 = Very strongly disagree, 50 = Neither agree nor
disagree, 100 = Very strongly agree).

*Estimates of future meat consumption.* Participants responded to 3
statements estimating the meat consumption of British people "THIS
year," "NEXT year," and "SIX years from now". The questions were
answered on a slider scale from 0-100%.

*Controlled variables.* To control for participants' background,
participants reported their political position (1 = very left wing, 7 =
very right wing), age, gender, and whether they were vegan or
vegetarian. We also measured conformity using 6 items from the
Iowa-Netherlands Comparison Orientation Measure (Gibbons & Buunk, 1999)
on a 7-point Likert scale (1 = strongly disagree, 7 = strongly agree).

# Results

## Overview {.tabset .tabset-pills}

### Randomization check

```{r rand-check, include = FALSE}
age_stat <- apa_print(aov(age ~ condition, clean)) # age
pol_stat <- apa_print(aov(politics ~ condition, clean)) # political position
gender_stat <- apa_print(chisq.test(clean$condition, clean$gender), n = nrow(clean)) # gender
nation_stat <- apa_print(chisq.test(clean$condition, clean$country), n = nrow(clean)) # nation
```

A preliminary randomization check was conducted. The check revealed no
systematic differences between the three conditions in gender, age,
political position, and home country (all *p*'s \> .05).

### Reliability and inter-correlations

```{r correlation, results = "asis"}
measure.tib %>%
  kable(caption = "Means (M), standard deviations (SD), and inter-correlations among study measures.", col.names = c("Measure", "$M$", "$SD$", 1:5), digits = 2, escape = F) %>% 
  add_header_above(c(" " = 3, "Correlations" = 5)) %>%
  kable_styling()
```

## Confirmatory Analyses

### Does trending norm (versus minority norm) information lead to more positive attitudes, intentions, interest, and expectations to limit own meat consumption?

```{r h1-desc, results = "asis"}
outcomes_desc <- clean %>%
  group_by(condition) %>%
  summarise(n = n(),
            m_interest = mean(interest),
            m_attitude = mean(attitude),
            m_int_exp = mean(expintent_avg),
            sd_interest = sd(interest),
            sd_attitude = sd(attitude),
            sd_int_exp = sd(expintent_avg), .groups = "rowwise") %>% printnum()

outcomes_tab <- paste(unlist(outcomes_desc[3:5]), unlist(outcomes_desc[6:8]), sep = ' $\\pm$ ')

outcomes.tib <- tibble(Measure = c("1. Interest", "2. Attitude", "3. Intention/Expectation"),
                       Dynamic = unlist(outcomes_tab[c(1,4,7)]),
                       Static = unlist(outcomes_tab[c(2,5,8)]),
                       None     = unlist(outcomes_tab[c(3,6,9)]))

outcomes.tib %>%
  kable(caption = "Outcomes by condition ($M$ $\\pm$ $SD$)", digits = 2, escape = F) %>% 
  add_header_above(c(" " = 1, "Conditions" = 3)) %>%
  kable_styling()
```

```{r h1-analysis, include=FALSE}
# model
h1.mod <- '
interest  ~ static + none
attitude  ~ static + none
expintent_avg ~ static + none'

h1.fit <- sem(model = h1.mod, data = clean)
h1.out <-  summary(h1.fit, standardized = T, ci = T, fit.measures = T, rsq = T)

h1.effect <- sapply(1:6, function(x) bfrr(-1*h1.out$PE[x, 5],h1.out$PE[x,6], sample_df = h1.out$FIT["ntotal"] - 1, model = "normal", mean = 0, sd = 5, tail = 1, criterion = 3,
                                          rr_interval = list(mean = c(-15, 15), sd = c(0, 15)), precision = 0.05))[-14,] # effect sizes

h1.rr <- sapply(1:6, function(x) paste0("HN[", toString(h1.effect[,x]$RR$sd), "]"))

h1.table <- cbind(h1.out$PE[1:6,c(1, 3, 5, 12, 6:10)], unlist(h1.effect[3,]), h1.rr, unlist(h1.effect[5,])) %>% 
  .[with(., order(rhs, decreasing = TRUE)), ] %>% 
  select(., -2) %>%
  mutate(pvalue = printp(pvalue))
```

```{r h1-table, results='asis'}
h1.table %>% 
  kable(caption = "Path model (outcomes ~ condition)", row.names = F, escape = F, col.names = c("Model path", "$\\beta$", "$B$", "$SE$", "$z$", "$\\textit{p}$", "$LL$", "$UL$", "$B_{{H}(0, 5)}$", "RR", "Conclusion$^a$"), digits = 2) %>%
  add_header_above(c(" " = 6, "95% CI" = 2, "Bayesian inference" = 3)) %>%
  kable_styling() %>%
  pack_rows("Trending vs. minority", 1, 3) %>%
  pack_rows("Trending vs. none", 4, 6) %>%
  footnote(general_title = "Note.",
           general = paste0("CI = confidence interval; $LL$ = lower limit; $UL$ = upper limit. Model fit: $\\chi^2$(", h1.out$FIT[["baseline.df"]], ", N = ", h1.out$FIT[["ntotal"]], ") = ", round(h1.out$FIT[["baseline.chisq"]],2), ", $\\textit{p}$ ",
                            printp(h1.out$FIT[["baseline.pvalue"]]), "; CFI = ", printnum(h1.out$FIT[["cfi"]]), "; RMSEA = ", printnum(h1.out$FIT[["rmsea"]])),
           alphabet = c("H0 = evidence for null hypothesis, no = no conclusion, H1 = evidence for alternative hypothesis."),
           footnote_as_chunk = T)
```

```{r h1-plots, fig.cap = "Violin plots of outcome variables by condition"}
out_plots <- clean %>%
  select(-intention, -expectation)  %>%
  pivot_longer(cols = c("interest", "attitude", "expintent_avg"), names_to = "variable", values_to = "value") %>%
  ggplot(aes(x = condition, y = value)) +
  facet_wrap(~ variable, labeller = as_labeller(c('attitude'="Attitude", 'expintent_avg'="Intention/Expectation", 'interest'="Interest"))) +
  geom_violin(trim = FALSE) + 
  stat_summary(fun.data = "mean_sdl",  fun.args = list(mult = 1), geom = "pointrange", color = "black") +
  ggtitle("Distribution of outcomes by condition") +
  xlab("Norm Condition") +
  ylab("Value (%)") +
  scale_x_discrete(limits = c("dynamic", "static", "none"), labels=c("dynamic" = "Dynamic", "static" = "Static","none" = "None")) +
  papaja::theme_apa()

#ggsave(file="out_dist.svg", plot=out_plots)
out_plots
```

### Will participants in the trending minority norm condition be more likely (than minority norm only) to expect a decrease in meat consumption by British people?

```{r h2-analysis, include = FALSE}
cons_desc <- clean %>%
  group_by(condition) %>%
  summarise(n = n(),
            m_current = mean(cons_now_perc),
            m_next = mean(cons_next_perc),
            m_six = mean(cons_six_perc),
            m_composite = mean(cons_proj),
            sd_current = sd(cons_now_perc),
            sd_next = sd(cons_next_perc),
            sd_six = sd(cons_six_perc),
            sd_composite = sd(cons_proj), .groups = "rowwise")

h2.test <- apa_print(aov(cons_proj ~ condition, clean)) 
```

```{r h2-table, results = "asis"}
cons_desc[c(1:2, 6, 10)] %>%
  kable(caption = "Projected consumption average by condition", col.names = c("Condition", "n",  "$M$", "$SD$"), escape = F, digits = 2) %>% 
  kable_styling() %>%
  footnote(general_title = "Note.",
           general = h2.test$full_result$condition,
           footnote_as_chunk = T)
```

### Does the perceived current and future popularity of sustainable eating behaviours correlate with interest, attitudes, expectations, and intentions to limit own meat consumption?

```{r h3-analysis, include = FALSE}
h3.mod <- '
interest  ~ cons_proj
attitude  ~ cons_proj
expintent_avg ~ cons_proj'

h3.fit <- sem(model = h3.mod, data = clean)
h3.out <-  summary(h3.fit, standardized = T, ci = T, fit.measures = T, rsq = T)

h3.effect <- sapply(1:3, function(x) bfrr(h3.out$PE[x, 5],h3.out$PE[x,6], sample_df = h3.out$FIT["ntotal"] - 1, model = "normal", mean = 0, sd = 5, tail = 1, criterion = 3,
                                          rr_interval = list(mean = c(-15, 15), sd = c(0, 15)), precision = 0.05))[-14,] # effect sizes

h3.rr <- sapply(1:3, function(x) paste0("HN[", toString(h3.effect[,x]$RR$sd), "]"))

h3.table <- cbind(h3.out$PE[1:3, c(1, 3, 5, 11, 6:10)], unlist(h3.effect[3,]), h3.rr, unlist(h3.effect[5,])) %>% select(., -2) %>%
  mutate(pvalue = printp(pvalue))
```

```{r h3-table, results='asis'}
h3.table %>% 
  kable(caption = "Path model (outcomes ~ projected consumption)", row.names = F, escape = F, col.names = c("Model path", "$\\beta$", "$B$", "$SE$", "$z$", "$\\textit{p}$", "$LL$", "$UL$", "$B_{{H}(0, 5)}$", "RR", "Conclusion$^a$"), digits = 2) %>%
  add_header_above(c(" " = 6, "95% CI" = 2, "Bayesian inference" = 3)) %>%
  kable_styling() %>%
  footnote(general_title = "Note.",
           general = paste0("CI = confidence interval; $LL$ = lower limit; $UL$ = upper limit. Model fit: $\\chi^2($", h3.out$FIT[["baseline.df"]], ", N = ", h3.out$FIT[["ntotal"]], ") = ", round(h3.out$FIT[["baseline.chisq"]],2), ", $\\textit{p}$ ",
                            printp(h3.out$FIT[["baseline.pvalue"]]), "; CFI = ", printnum(h3.out$FIT[["cfi"]]), "; RMSEA = ", printnum(h3.out$FIT[["rmsea"]])),
           alphabet = c("H0 = evidence for null hypothesis, no = no conclusion, H1 = evidence for alternative hypothesis."),
           footnote_as_chunk = T)
```

## Exploratory Analyses

### Is projected meat consumption a mediator of the effect of trending minority norms vs. minority only on meat consumption outcomes?

```{r h4-analysis, include = FALSE}
h4.mod <- '
interest  ~ a*cons_proj + b*static
attitude  ~ c*cons_proj + d*static
expintent_avg ~ e*cons_proj + f*static
cons_proj ~ t*static

ta := t*a
tc := t*c
te := t*e
totint := ta + b
totatt := tc + d
totintent := te + f'

h4.fit <- sem(h4.mod,data=clean, se="bootstrap", test="bootstrap", bootstrap = 5000, meanstructure=TRUE)
h4.out <- summary(h4.fit, standardized = T, ci = T, fit.measures = T)
h4.pam <- parameterEstimates(h4.fit)

h4.table <- h4.out$PE[c(1:7, 21:26),c(1, 3, 6, 13, 7:11)] %>% .[with(., order(rhs, decreasing = FALSE)), ]
h4.table <- rbind("", h4.table[1:3,], "", h4.table[4:13,] ) %>%
  mutate_at(vars(3:9), ~as.numeric(as.character(.))) %>%
  mutate(pvalue = printp(pvalue),
         lhs = c("~ Projected consumption", "Interest", "Attitude", "Intention/Expectation", 
                 "~ Condition", "Interest", "Attitude", "Intention/Expectation", "Projected consumption", 
                 "Interest", "Attitude", "Intention/Expectation", "Interest", "Attitude", "Intention/Expectation")) %>% 
  select(., -2) # effect sizes
```

```{r h4-table, results='asis'}
h4.table %>% 
  kable(caption = "Mediation model", row.names = F, escape = F, col.names = c("Model path", "$\\beta$", "$B$", "$SE$", "$z$", "$\\textit{p}$", "$LL$", "$UL$"), digits = 2) %>%
  add_header_above(c(" " = 6, "95% CI" = 2)) %>%
  kable_styling() %>%
  pack_rows("Direct effects", 1, 9) %>%
  pack_rows("Indirect effects (~ condition > projected consumption)", 10, 12) %>%
  pack_rows("Total effects (~ condition + condition > projected consumption)", 13, 15) %>%
  footnote(general_title = "Note.",
           general = paste0("CI = confidence interval; $LL$ = lower limit; $UL$ = upper limit. Model fit: $\\chi^2$(", h4.out$FIT[["baseline.df"]], ", N = ", h4.out$FIT[["ntotal"]], ") = ", round(h4.out$FIT[["baseline.chisq"]],2), ", $\\textit{p}$ ",
                            printp(h4.out$FIT[["baseline.pvalue"]]), "; CFI = ", printnum(h4.out$FIT[["cfi"]]), "; RMSEA = ", printnum(h4.out$FIT[["rmsea"]])),
           footnote_as_chunk = T)
```

```{r h4-plot, fig.cap = "Relationship between projected consumption and outcomes"}
scat_plots <- clean %>%
  select(-intention, -expectation)  %>%
  pivot_longer(cols = c("interest", "attitude", "expintent_avg"), names_to = "variable", values_to = "value") %>%
  ggplot(aes(x = cons_proj, y = value)) +
  facet_wrap(~ variable, labeller = as_labeller(c('attitude'="Attitude", 'expintent_avg'="Intent/Expectation", 'interest'="Interest"))) +
  geom_smooth(aes(color = condition), method = loess, se = F) +
  stat_summary(fun.data = "mean_cl_boot", geom = "point", size = 0.5, alpha = 0.4) +
  ggtitle("Relationship between projected consumption and outcome variables") +
  xlab("Projected consumption (% limiting meat eating)") +
  ylab("Value of outcome (%)") +
  papaja::theme_apa()

#ggsave(file="corr_scat.svg", plot=scat_plots)

scat_plots
```

### How do demographic factors such as age, gender, and political position predict primary dependent variables relating to meat consumption?

```{r h5-analysis, include=FALSE}
h5.mod <- '
interest  ~ static + cons_proj + age_c + genderbi + politics
attitude  ~ static + cons_proj + age_c + genderbi + politics
expintent_avg ~ static + cons_proj + age_c + genderbi + politics'

h5.fit <- sem(model = h5.mod, data = clean)
h5.out <- summary(h5.fit, standardized = T, ci = T, fit.measures = T, rsq = T)

h5.table <- h5.out$PE[1:15,c(3, 5, 12, 6:10)] %>%
  mutate(pvalue = printp(pvalue),
         rhs = rep(c("Condition$^a$", "Projected consumption", "Age", "Gender$^b$", "Politics$^c$"), 3))
```

```{r h5-table, results='asis'}
h5.table %>% 
  kable(caption = "Full model", row.names = F, escape = F, col.names = c("Model path", "$\\beta$", "$B$", "$SE$", "$z$", "$\\textit{p}$", "$LL$", "$UL$"), digits = 2) %>%
  add_header_above(c(" " = 6, "95% CI" = 2)) %>%
  kable_styling() %>%
  pack_rows(paste0("Interest ~ ($R$ = ", scales::percent(h5.out$PE[37,5]), ")"), 1, 5) %>%
  pack_rows(paste0("Attitude ~ ($R$ = ", scales::percent(h5.out$PE[38,5]), ")"), 6, 10) %>%
  pack_rows(paste0("Intention/Expectation ~ ($R$ = ", scales::percent(h5.out$PE[39,5]), ")"), 11, 15) %>%
  footnote(general_title = "Note.",
           general = paste0("CI = confidence interval; $LL$ = lower limit; $UL$ = upper limit. Model fit: $\\chi^2$(", h5.out$FIT[["baseline.df"]], ", N = ", h5.out$FIT[["ntotal"]], ") = ", round(h5.out$FIT[["baseline.chisq"]],2), ", $\\textit{p}$ ",
                            printp(h5.out$FIT[["baseline.pvalue"]]), "; CFI = ", printnum(h5.out$FIT[["cfi"]]), "; RMSEA = ", printnum(h5.out$FIT[["rmsea"]])),
           alphabet = c("Trending compared to minority norms; ", "Binary coded, 0 = Male, 1 = Female; ", "Scaled from left to right wing"))
```

### Does conformity moderate the effects of the trend condition on interest in eating less meat?

# Codebook

```{r codebook}
codebook::codebook_table(clean)
```
